Guilt, shame, and anti-war action in an authoritarian country at war

### 2023-04-30 manuscript.Rmd
Switched to p_format for formatting p-values

packagelist <- c('readr','psych','GPArotation','lavaan','pscl','ggplot2','sjPlot', 'car','dplyr','MASS','writexl','readxl','kableExtra')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

rms_table1 <- NULL
rms_table1[1] <- round(summary_tablems$r.squared,digits=3)
rms_table1[2] <- round(summary_tableis$r.squared,digits=3)
rms_table1[3] <- round(summary_tableg$r.squared,digits=3)

#create matrix to contain the numbers of table 1
table1_numbers <- data.frame(matrix(nrow=7, ncol=12))
#add beta ms
table1_numbers[1:6,1] <- round(h1ms2$coefficients, digits = 2)
#add b ms
table1_numbers[1:6,2] <- round(h1ms$coefficients, digits = 2)
#add se ms
table1_numbers[1:6,3] <- round(summary_tablems$coefficients[1:6,2], digits = 2)
#add p values ms
table1_numbers[1:6,4] <- format.pval(summary_tablems$coefficients[1:6,4], digits = 2, eps = 0.001, nsmall = 3)

#add beta is
table1_numbers[1:6,5] <- round(h1is2$coefficients, digits = 2)
#add b is
table1_numbers[1:6,6] <- round(h1is$coefficients, digits = 2)
#add se is
table1_numbers[1:6,7] <- round(summary_tableis$coefficients[1:6,2], digits = 2)
#add p values is
table1_numbers[1:6,8] <- format.pval(summary_tableis$coefficients[1:6,4], digits = 2, eps = 0.001, nsmall = 3)

#add beta g
table1_numbers[1:6,9] <- round(h1g2$coefficients, digits = 2)
#add b g
table1_numbers[1:6,10] <- round(h1g$coefficients, digits = 2)
#add se g
table1_numbers[1:6,11] <- round(summary_tableg$coefficients[1:6,2], digits = 2)
#add p values g
table1_numbers[1:6,12] <- format.pval(summary_tableg$coefficients[1:6,4], digits = 2, eps = 0.001, nsmall = 3)

@@

knitr::kable(table1_numbers, caption='Predicting group-based guilt and shame from political beliefs',align='lcccccccccccc', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>% 
  kableExtra::add_header_above(c("", "Moral Shame" = 4, "Image Shame" = 4, "Guilt" = 4)) %>%
  row_spec(6,hline_after=T)

@@

rms_table2 <- NULL
rms_table2[1] <- round(summary_table3a$r.squared,digits=3)
rms_table2[2] <- round(summary_table3b$r.squared,digits=3)
rms_table2[3] <- round(summary_table3c$r.squared,digits=3)

#create matrix to contain the numbers of table 2
table2_numbers <- matrix(nrow=5, ncol=12)
#add beta 3a
table2_numbers[1:4,1] <- round(h3a2$coefficients, digits = 2)
#add b ms
table2_numbers[1:4,2] <- round(h3a$coefficients, digits = 2)
#add se ms
table2_numbers[1:4,3] <- round(summary_table3a$coefficients[1:4,2], digits = 2)
#add p values ms
table2_numbers[1:4,4] <- format.pval(summary_table3a$coefficients[1:4,4], digits = 2, eps = 0.001, nsmall = 3)

#add beta 3b
table2_numbers[1:4,5] <- round(h3b2$coefficients, digits = 2)
#add b is
table2_numbers[1:4,6] <- round(h3b$coefficients, digits = 2)
#add se is
table2_numbers[1:4,7] <- round(summary_table3b$coefficients[1:4,2], digits = 2)
#add p values is
table2_numbers[1:4,8] <- format.pval(summary_table3b$coefficients[1:4,4], digits = 2, eps = 0.001, nsmall = 3)

#add beta 3c
table2_numbers[1:4,9] <- round(h3c2$coefficients, digits = 2)
#add b g
table2_numbers[1:4,10] <- round(h3c$coefficients, digits = 2)
#add se g
table2_numbers[1:4,11] <- round(summary_table3c$coefficients[1:4,2], digits = 2)
#add p values g
table2_numbers[1:4,12] <- format.pval(summary_table3c$coefficients[1:4,4], digits = 2, eps = 0.001, nsmall = 3)

@@

knitr::kable(table2_numbers, caption='Predicting anti-war action from group-based guilt and shame', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>% 
  kableExtra::add_header_above(c("", "Past Behaviour" = 4, "Behavioural Intention" = 4, "Action Probability" = 4)) %>%
  row_spec(4,hline_after=T)

@@

```{r table3-numbers}
#save summary of h4
summary_tableh4 <- summary(h4)

#create matrix to contain the numbers of table 1
table3_numbers <- matrix(nrow=8, ncol=5)
#add beta 
table3_numbers[1:8,1] <- round(h42$coefficients, digits = 3)
#add b 
table3_numbers[1:8,2] <- round(h4$coefficients, digits = 2)
#add se 
table3_numbers[1:8,3] <- round(summary_tableh4$coefficients[1:8,2], digits = 2)
#add t 
table3_numbers[1:8,4] <- round(summary_tableh4$coefficients[1:8,3], digits = 2)
#add p values
table3_numbers[1:8,5] <- format.pval(summary_tableh4$coefficients[1:8,4], digits = 2, eps = 0.001, nsmall = 3)

@@

Behavioral intentions and action probability correlated at *r* = `r round(correlation1$estimate, digits = 2)`, *p* `r format.pval(correlation1$p.value, digits = 2, eps = 0.001, nsmall = 3)`, so we scaled and combined the two measures into a single indicator of future anti-war action. We ran a linear regression predicting future anti-war behavior from attitude towards the war, negative and positive emotions, and shame and guilt. Table \@ref(tab:Table3) presents the results. Overall, the model explained `r round(100*summary_tableh4$adj.r.squared)`% of variance in future behavior. Anti-war behavioral intentions were best predicted by moral shame ($\beta$ = `r round(h42$coefficients[6], digits = 2)`, *p* `r format.pval(summary_tableh4$coefficients[6,4], digits = 2, eps = 0.001, nsmall = 3)`), followed by negative dominant emotions ($\beta$ = `r round(h42$coefficients[3], digits = 2)`, *p* `r format.pval(summary_tableh4$coefficients[3,4], digits = 2, eps = 0.001, nsmall = 3)`), and only then attitude ($\beta$ = `r round(h42$coefficients[5], digits = 2)`, *p* `r format.pval(summary_tableh4$coefficients[5,4], digits = 2, eps = 0.001, nsmall = 3)`). Negative submissive emotions had a small negative effect on intentions to act ($\beta$ = `r round(h42$coefficients[4], digits = 2)`, *p* = `r format.pval(summary_tableh4$coefficients[4,4], digits = 2, eps = 0.001, nsmall = 3)`).

@@

knitr::kable(table3_numbers, caption='Predicting future behavior from emotions and attitudes
', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position")

@@

The results of the zero-inflated negative binomial model (Table \@ref(tab:TableS4), SM) suggested that different predictors account for the presence vs. absence of intentions to act versus the strength of these intentions. Only moral shame (*b* = `r round(S4$coefficients$zero[6,1],digits=2)`, *p* = `r round(S4$coefficients$zero[6,4],digits=3)`) and attitude (*b* = `r round(S4$coefficients$zero[5,1],digits=2)`, *p* = `r round(S4$coefficients$zero[5,4],digits=3)`) predicted the probability of no action, whereas only negative emotions predicted the strength of these intentions. Negative dominant emotions predicted stronger intentions to act (*b* = `r round(S4$coefficients$count[3,1],digits=2)`, *p* = <0.001), whereas negative submissive emotions predicted weaker intentions to act (*b* = `r round(S4$coefficients$count[4,1],digits=2)`, *p* = `r round(S4$coefficients$count[4,4],digits=3)`).

@@

tableS1_numbers <- matrix(0,nrow=18,ncol=5)
tableS1_numbers[c(2:6,8:12,14:18),1] <- round(S1data$pe$est[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),2] <- round(S1data$pe$se[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),3] <- round(S1data$pe$z[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),4] <- round(S1data$pe$pvalue[1:15],digits=3)
tableS1_numbers[c(2:6,8:12,14:18),5] <- round(S1data$pe$std.all[1:15],digits=2)

tableS1_numbers[which(tableS1_numbers==0)] <- '<0.001'
tableS1_numbers[c(1,7,13),] <- ' '

@@

tableS2_numbers <- matrix(0,nrow=14,ncol=9)
tableS2_numbers[1,] <- ' '
tableS2_numbers[2:7,1:2] <- round(ms$coefficients$count[1:6,1:2],digits=2)
tableS2_numbers[2:7,3] <- round(ms$coefficients$count[1:6,4],digits=3)
tableS2_numbers[2:7,4:5] <- round(is$coefficients$count[1:6,1:2],digits=2)
tableS2_numbers[2:7,6] <- round(is$coefficients$count[1:6,4],digits=3)
tableS2_numbers[2:7,7:8] <- round(gu$coefficients$count[1:6,1:2],digits=2)
tableS2_numbers[2:7,9] <- round(gu$coefficients$count[1:6,4],digits=3)
tableS2_numbers[8,] <- ' '
tableS2_numbers[9:14,1:2] <- round(ms$coefficients$zero[1:6,1:2],digits=2)
tableS2_numbers[9:14,3] <- round(ms$coefficients$zero[1:6,4],digits=3)
tableS2_numbers[9:14,4:5] <- round(is$coefficients$zero[1:6,1:2],digits=2)
tableS2_numbers[9:14,6] <- round(is$coefficients$zero[1:6,4],digits=3)
tableS2_numbers[9:14,7:8] <- round(gu$coefficients$zero[1:6,1:2],digits=2)
tableS2_numbers[9:14,9] <- round(gu$coefficients$zero[1:6,4],digits=3)

tableS2_numbers[which(tableS2_numbers==0)] <- '<0.001'

@@

tableS3_numbers <- matrix(0,nrow=10,ncol=9)
tableS3_numbers[1,] <- ' '
tableS3_numbers[2:5,1:2] <- round(S3a$coefficients$count[1:4,1:2],digits=2)
tableS3_numbers[2:5,3] <- round(S3a$coefficients$count[1:4,4],digits=3)
tableS3_numbers[2:5,4:5] <- round(S3b$coefficients$count[1:4,1:2],digits=2)
tableS3_numbers[2:5,6] <- round(S3b$coefficients$count[1:4,4],digits=3)
tableS3_numbers[2:5,7:8] <- round(S3c$coefficients$count[1:4,1:2],digits=2)
tableS3_numbers[2:5,9] <- round(S3c$coefficients$count[1:4,4],digits=3)
tableS3_numbers[6,] <- ' '
tableS3_numbers[7:10,1:2] <- round(S3a$coefficients$zero[1:4,1:2],digits=2)
tableS3_numbers[7:10,3] <- round(S3a$coefficients$zero[1:4,4],digits=3)
tableS3_numbers[7:10,4:5] <- round(S3b$coefficients$zero[1:4,1:2],digits=2)
tableS3_numbers[7:10,6] <- round(S3b$coefficients$zero[1:4,4],digits=3)
tableS3_numbers[7:10,7:8] <- round(S3c$coefficients$zero[1:4,1:2],digits=2)
tableS3_numbers[7:10,9] <- round(S3c$coefficients$zero[1:4,4],digits=3)

tableS3_numbers[which(tableS3_numbers[,3]==0),3] <- '<0.001'
tableS3_numbers[which(tableS3_numbers[,6]==0),6] <- '<0.001'
tableS3_numbers[which(tableS3_numbers[,9]==0),9] <- '<0.001'

@@

tableS4_numbers <- matrix(0,nrow=18,ncol=4)
tableS4_numbers[1,] <- ' '
tableS4_numbers[2:9,1:3] <- round(S4$coefficients$count[1:8,1:3],digits=2)
tableS4_numbers[2:9,4] <- round(S4$coefficients$count[1:8,4],digits=3)
tableS4_numbers[10,] <- ' '
tableS4_numbers[11:18,1:3] <- round(S4$coefficients$zero[1:8,1:3],digits=2)
tableS4_numbers[11:18,4] <- round(S4$coefficients$zero[1:8,4],digits=3)

tableS4_numbers[which(tableS4_numbers[,3]==0),3] <- '<0.01'
tableS4_numbers[which(tableS4_numbers[,4]==0),4] <- '<0.001'

>>>>

packagelist <- c('readr','psych','GPArotation','lavaan','pscl','ggplot2','sjPlot', 'car','dplyr','MASS','writexl','readxl','kableExtra','rstatix')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

rms_table1 <- c(summary_tablems$r.squared,summary_tableis$r.squared,summary_tableg$r.squared)
rms_table1 <- p_format(rms_table1, leading.zero = FALSE, digits=3, trailing.zero=TRUE, accuracy=0.001)

#create matrix to contain the numbers of table 1
table1_numbers <- data.frame(matrix(nrow=7, ncol=12))
#add beta ms
table1_numbers[1:6,1] <- round(h1ms2$coefficients, digits = 2)
#add b ms
table1_numbers[1:6,2] <- round(h1ms$coefficients, digits = 2)
#add se ms
table1_numbers[1:6,3] <- round(summary_tablems$coefficients[1:6,2], digits = 2)
#add p values ms
table1_numbers[1:6,4] <- p_format(summary_tablems$coefficients[1:6,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)

#add beta is
table1_numbers[1:6,5] <- round(h1is2$coefficients, digits = 2)
#add b is
table1_numbers[1:6,6] <- round(h1is$coefficients, digits = 2)
#add se is
table1_numbers[1:6,7] <- round(summary_tableis$coefficients[1:6,2], digits = 2)
#add p values is
table1_numbers[1:6,8] <- p_format(summary_tableis$coefficients[1:6,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)

#add beta g
table1_numbers[1:6,9] <- round(h1g2$coefficients, digits = 2)
#add b g
table1_numbers[1:6,10] <- round(h1g$coefficients, digits = 2)
#add se g
table1_numbers[1:6,11] <- round(summary_tableg$coefficients[1:6,2], digits = 2)
#add p values g
table1_numbers[1:6,12] <- p_format(summary_tableg$coefficients[1:6,4], leading.zero = FALSE,digits=2,trailing.zero=TRUE,accuracy=0.001)

@@

knitr::kable(table1_numbers, caption='Predicting group-based guilt and shame from political beliefs',align='rrrrrrrrrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>% 
  kableExtra::add_header_above(c("", "Moral Shame" = 4, "Image Shame" = 4, "Guilt" = 4)) %>%
  row_spec(6,hline_after=T)

@@

rms_table2 <- c(summary_table3a$r.squared,summary_table3b$r.squared,summary_table3c$r.squared)
rms_table2 <- p_format(rms_table2, leading.zero = FALSE, digits=3, trailing.zero=TRUE, accuracy=0.001)

#create matrix to contain the numbers of table 2
table2_numbers <- matrix(nrow=5, ncol=12)
#add beta 3a
table2_numbers[1:4,1] <- round(h3a2$coefficients, digits = 2)
#add b ms
table2_numbers[1:4,2] <- round(h3a$coefficients, digits = 2)
#add se ms
table2_numbers[1:4,3] <- round(summary_table3a$coefficients[1:4,2], digits = 2)
#add p values ms
table2_numbers[1:4,4] <- p_format(summary_table3a$coefficients[1:4,4], leading.zero = FALSE,digits=1,trailing.zero=TRUE,accuracy=0.001)

#add beta 3b
table2_numbers[1:4,5] <- round(h3b2$coefficients, digits = 2)
#add b is
table2_numbers[1:4,6] <- round(h3b$coefficients, digits = 2)
#add se is
table2_numbers[1:4,7] <- round(summary_table3b$coefficients[1:4,2], digits = 2)
#add p values is
table2_numbers[1:4,8] <- p_format(summary_table3b$coefficients[1:4,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)

#add beta 3c
table2_numbers[1:4,9] <- round(h3c2$coefficients, digits = 2)
#add b g
table2_numbers[1:4,10] <- round(h3c$coefficients, digits = 2)
#add se g
table2_numbers[1:4,11] <- round(summary_table3c$coefficients[1:4,2], digits = 2)
#add p values g
table2_numbers[1:4,12] <- p_format(summary_table3c$coefficients[1:4,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)

@@

knitr::kable(table2_numbers, caption='Predicting anti-war action from group-based guilt and shame', align='rrrrrrrrrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>% 
  kableExtra::add_header_above(c("", "Past Behaviour" = 4, "Behavioural Intention" = 4, "Action Probability" = 4)) %>%
  row_spec(4,hline_after=T)

@@

```{r table3_numbers, echo=FALSE, include=FALSE}

#save summary of h4
summary_tableh4 <- summary(h4)

#create matrix to contain the numbers of table 1
table3_numbers <- matrix(nrow=8, ncol=5)
#add beta 
table3_numbers[1:8,1] <- round(h42$coefficients, digits = 3)
#add b 
table3_numbers[1:8,2] <- round(h4$coefficients, digits = 2)
#add se 
table3_numbers[1:8,3] <- round(summary_tableh4$coefficients[1:8,2], digits = 2)
#add t 
table3_numbers[1:8,4] <- round(summary_tableh4$coefficients[1:8,3], digits = 2)
#add p values
table3_numbers[1:8,5] <- p_format(summary_tableh4$coefficients[1:8,4], leading.zero = FALSE,digits=2,trailing.zero=TRUE,accuracy=0.001)

@@

Behavioral intentions and action probability correlated at *r* = `r round(correlation1$estimate, digits = 2)`, *p* `r p_format(correlation1$p.value, leading.zero = FALSE,digits=3,accuracy=0.001)`, so we scaled and combined the two measures into a single indicator of future anti-war action. We ran a linear regression predicting future anti-war behavior from attitude towards the war, negative and positive emotions, and shame and guilt. Table \@ref(tab:Table3) presents the results. Overall, the model explained `r round(100*summary_tableh4$adj.r.squared)`% of variance in future behavior. Anti-war behavioral intentions were best predicted by moral shame ($\beta$ = `r round(h42$coefficients[6], digits = 2)`, *p* `r p_format(summary_tableh4$coefficients[6,4], leading.zero = FALSE,digits=3,accuracy=0.001)`), followed by negative dominant emotions ($\beta$ = `r round(h42$coefficients[3], digits = 2)`, *p* `r p_format(summary_tableh4$coefficients[3,4], leading.zero = FALSE,digits=3,accuracy=0.001)`), and only then attitude ($\beta$ = `r round(h42$coefficients[5], digits = 2)`, *p* `r p_format(summary_tableh4$coefficients[5,4], leading.zero = FALSE,digits=3,accuracy=0.001)`). Negative submissive emotions had a small negative effect on intentions to act ($\beta$ = `r round(h42$coefficients[4], digits = 2)`, *p* = `r p_format(summary_tableh4$coefficients[4,4], leading.zero = FALSE,digits=2,accuracy=0.001)`).

@@

knitr::kable(table3_numbers, caption='Predicting future behavior from emotions and attitudes
', align='rrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position")

@@

The results of the zero-inflated negative binomial model (Table \@ref(tab:TableS4), SM) suggested that different predictors account for the presence vs. absence of intentions to act versus the strength of these intentions. Only moral shame (*b* = `r round(S4$coefficients$zero[6,1],digits=2)`, *p* = `r p_format(S4$coefficients$zero[6,4], leading.zero = FALSE,digits=2,accuracy=0.001)`) and attitude (*b* = `r round(S4$coefficients$zero[5,1],digits=2)`, *p* = `r p_format(S4$coefficients$zero[5,4], leading.zero = FALSE,digits=1,accuracy=0.001)`) predicted the probability of no action, whereas only negative emotions predicted the strength of these intentions. Negative dominant emotions predicted stronger intentions to act (*b* = `r round(S4$coefficients$count[3,1],digits=2)`, *p* = `r p_format(S4$coefficients$count[3,4], leading.zero = FALSE,digits=2,accuracy=0.001)`), whereas negative submissive emotions predicted weaker intentions to act (*b* = `r round(S4$coefficients$count[4,1],digits=2)`, *p* = `r p_format(S4$coefficients$count[4,4], leading.zero = FALSE,digits=2,accuracy=0.001)`).

@@

tableS1_numbers <- matrix(0,nrow=18,ncol=5)
tableS1_numbers[c(2:6,8:12,14:18),1] <- round(S1data$pe$est[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),2] <- round(S1data$pe$se[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),3] <- round(S1data$pe$z[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),4] <- p_format(S1data$pe$pvalue[1:15], leading.zero = FALSE,digits=2,accuracy=0.001)
tableS1_numbers[c(2:6,8:12,14:18),5] <- round(S1data$pe$std.all[1:15],digits=2)

tableS1_numbers[c(1,7,13),] <- ' '

@@

tableS2_numbers <- matrix(0,nrow=14,ncol=9)
tableS2_numbers[1,] <- ' '
tableS2_numbers[2:7,1:2] <- round(ms$coefficients$count[1:6,1:2],digits=2)
tableS2_numbers[2:7,3] <- p_format(ms$coefficients$count[1:6,4], leading.zero = FALSE,digits=1,trailing.zero=TRUE,accuracy=0.001)
tableS2_numbers[2:7,4:5] <- round(is$coefficients$count[1:6,1:2],digits=2)
tableS2_numbers[2:7,6] <- p_format(is$coefficients$count[1:6,4], leading.zero = FALSE,digits=1,trailing.zero=TRUE,accuracy=0.001)
tableS2_numbers[2:7,7:8] <- round(gu$coefficients$count[1:6,1:2],digits=2)
tableS2_numbers[2:7,9] <- p_format(gu$coefficients$count[1:6,4], leading.zero = FALSE,digits=2,trailing.zero=TRUE,accuracy=0.001)
tableS2_numbers[8,] <- ' '
tableS2_numbers[9:14,1:2] <- round(ms$coefficients$zero[1:6,1:2],digits=2)
tableS2_numbers[9:14,3] <- p_format(ms$coefficients$zero[1:6,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)
tableS2_numbers[9:14,4:5] <- round(is$coefficients$zero[1:6,1:2],digits=2)
tableS2_numbers[9:14,6] <- p_format(is$coefficients$zero[1:6,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)
tableS2_numbers[9:14,7:8] <- round(gu$coefficients$zero[1:6,1:2],digits=2)
tableS2_numbers[9:14,9] <- p_format(gu$coefficients$zero[1:6,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)

@@

tableS3_numbers <- matrix(0,nrow=10,ncol=9)
tableS3_numbers[1,] <- ' '
tableS3_numbers[2:5,1:2] <- round(S3a$coefficients$count[1:4,1:2],digits=2)
tableS3_numbers[2:5,3] <- p_format(S3a$coefficients$count[1:4,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)
tableS3_numbers[2:5,4:5] <- round(S3b$coefficients$count[1:4,1:2],digits=2)
tableS3_numbers[2:5,6] <- p_format(S3b$coefficients$count[1:4,4], leading.zero = FALSE,digits=1,trailing.zero=TRUE,accuracy=0.001)
tableS3_numbers[2:5,7:8] <- round(S3c$coefficients$count[1:4,1:2],digits=2)
tableS3_numbers[2:5,9] <- p_format(S3c$coefficients$count[1:4,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)
tableS3_numbers[6,] <- ' '
tableS3_numbers[7:10,1:2] <- round(S3a$coefficients$zero[1:4,1:2],digits=2)
tableS3_numbers[7:10,3] <- p_format(S3a$coefficients$zero[1:4,4], leading.zero = FALSE,digits=3,trailing.zero=TRUE,accuracy=0.001)
tableS3_numbers[7:10,4:5] <- round(S3b$coefficients$zero[1:4,1:2],digits=2)
tableS3_numbers[7:10,6] <- p_format(S3b$coefficients$zero[1:4,4], leading.zero = FALSE,digits=2,trailing.zero=TRUE,accuracy=0.001)
tableS3_numbers[7:10,7:8] <- round(S3c$coefficients$zero[1:4,1:2],digits=2)
tableS3_numbers[7:10,9] <- p_format(S3c$coefficients$zero[1:4,4], leading.zero = FALSE,digits=2,trailing.zero=TRUE,accuracy=0.001)

@@

tableS4_numbers <- matrix(0,nrow=18,ncol=4)
tableS4_numbers[1,] <- ' '
tableS4_numbers[2:9,1:3] <- round(S4$coefficients$count[1:8,1:3],digits=2)
tableS4_numbers[2:9,4] <- p_format(S4$coefficients$count[1:8,4], leading.zero = FALSE,digits=2,trailing.zero=TRUE,accuracy=0.001)
tableS4_numbers[10,] <- ' '
tableS4_numbers[11:18,1:3] <- round(S4$coefficients$zero[1:8,1:3],digits=2)
tableS4_numbers[11:18,4] <- p_format(S4$coefficients$zero[1:8,4], leading.zero = FALSE,digits=1,trailing.zero=TRUE,accuracy=0.001)

tableS4_numbers[which(tableS4_numbers[,3]==0),3] <- '<0.01'
